Reply To Examiners

### 2014-04-12 answer_thesis_examiner/chap3.tex
auto

There are apparently two main concerns from Examiner No. 3's comments.
First, page 44 line 1 should be intepreted strictly in the context of the preceeding paragraph (page 43). 
That is mathematically  speaking $\sigma$ is just a mathematical variables, thus making the statement true. 
Any resemblence of it with the SAR signal is established in the next paragraph.
The third line of the second paragraph in page 44 clearly indicated where $\sigma$ can be considered as constant (i.e. spatial homogeneous area or at each resolution cell).
It is also acknowledged in the thesis, as the Examiner No. 3 pointed out precisely: ``Over heterogeneous area, ... $\sigma$ varies significantly ...''
This is the assumption used in this analysis, 
  and a portion of subsequent work is devoted to extend this early analysis into heterogeneous area.
The very next section (i.e. Section 3.2) starts the discussion on this very topic.

In that very same vein, table 3.3 should be viewed under the assumption that $\sigma$ is constant (either in homogeneous area or in a single resolution cell).
Under this condition, then the variances are independent of $\sigma$, i.e. it is homoskedastic.
In fact, if the area is heterogeneous as reviewed in Chapter 2, there are many different ways to model $\sigma$ which in turns leads to many different models for the observable magnitude.
This, of course, leads to different expression for the observable variances.
In fact, it leads to heteroskedasticity, which the Examiner correctly pointed out ``$var(L_A)$ and $var(L_I)$ cannot be homoskedastic'', should we consider $var(L_I)$ as the variation of the observables in an area.
It should be noted, however, that at the level of each radar physical resolution cell, the values measured in SAR are not deterministic.
Then if we consider $var(L_A)$ as the deviation of the observables from its true signal, we will also have $var(L_A)$ as being constant (assuming that the effective number of looks or ENL is constant across the area)!

>>>>

There are apparently two main concerns from Examiner No. 3's comments.
The first is: ``how can the statement on page 44 line 1 ... be true?''.
And second: ``why homoskedasticity is valid, and what are the assumption in this analysis?''

First, the statement in page 44 line 1 should be intepreted strictly in the context of what preceeds it. 
That is mathematically  speaking $\sigma$ is just a mathematical constant, which makes the statement true. 
Any resemblence of it with the SAR signal is only established in the next paragraph onwards.
In fact, the third line of the second paragraph in page 44 clearly indicated where $\sigma$ can be considered as constant (i.e. spatial homogeneous area or at each resolution cell).
This is the assumption used in this analysis. 
The assumption is acknowledged in the very next sentence, as the Examiner No. 3 pointed out precisely: ``Over heterogeneous area, ... $\sigma$ varies significantly ...''.
If $\sigma$ is not a constant, then heteroskedastic ensues.
The next section (i.e. Section 3.2) then outlines the effects of heteroskedasticity, 
  which explains the needs for logarithmic transformation.

The assumption described above continues to hold in Section 3.3 and, of course, table 3.3.
%In that very same vein, table 3.3 should be viewed under the assumption that $\sigma$ is constant (either in homogeneous area or in a single resolution cell).
Under this condition, the variances of the log-transformed variables are then independent of $\sigma$.
The point being made in the table is that: 
  while variances are dependent on $\sigma$ in the original domain,
  in the log transformed domain, they are independent of this value.

The assumption actually is not very restrictive.
It should be noted that at the level of each radar physical resolution cell, 
  the value measured in SAR is not deterministic.
For all practical purposes, the single measured value is to be considered as the result of a stochastic process, with one ``true'' signal $\sigma$.
This model actually is applicable to both homogeneous and heterogeneous areas.

Now, if the area is heterogeneous, then $\sigma$ is no longer a constant.
In fact, as reviewed in Chapter 2, there are many different ways to model $\sigma$ which in turns leads to many different models for the observable magnitude.
%This, of course, leads to different expression for the observable variances.
This leads to heteroskedasticity, 
  which the Examiner correctly pointed out ``$var(L_A)$ and $var(L_I)$ cannot be homoskedastic'', 
  should we consider ``$var(L_A)$ and $var(L_I)$'' as the variation of the observables in an area.
However, if we consider ``$var(L_A)$ and $var(L_I)$'' as the deviation of the observables from corresponding its ``true'' signal at each physical resolution cell level, 
  then they will be independent of $\sigma$ (as described in Table 3.3).
In fact they are constant, even as $sigma$ changes.
This leads to homoskedasticity!
